Technique for \earlywarning\ detection of compact binary coalescence and its implication for multimessenger astronomy

### 2011-06-02 results.tex
added hist
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@816 ccdd05d5-56c1-461a-bf98-85f6876523b4
tweaked plot
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@817 ccdd05d5-56c1-461a-bf98-85f6876523b4
Added box and whisker plot
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@822 ccdd05d5-56c1-461a-bf98-85f6876523b4
Fixed macro
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@825 ccdd05d5-56c1-461a-bf98-85f6876523b4

In this section we test our implementation of the \lloid\ method using the
pipeline described in the previous section.  We answer the following questions
%
I) What is the measured loss of SNR due to the approximations used in the
\lloid\ algorithm in a realistic analysis pipeline?
%
II) What is the measured latency of the implementation described in section
\ref{sec:implementation}?
%
III) What is the measured computational cost of the implementation described in
section \ref{sec:implementation}?

@@

>>>>

In this section we test our implementation of the \lloid\ method using the
pipeline described in the previous section.  We answer the following questions
%
I) What is the measured loss of \SNR\ due to the approximations used in the
\lloid\ algorithm in a realistic analysis pipeline?
%
II) What is the measured latency of the implementation described in section
\ref{sec:implementation}?
%
III) What is the measured computational cost of the implementation described in
section \ref{sec:implementation}?

@@

\begin{figure}
	\label{fig:hist}
	\begin{center}
		\includegraphics{bw.pdf}
		\caption{Box-and-whisker plot of mismatch between nominal template bank and \lloid\ measured impulse respones.  The \textsc{svd} tolerance is varied from $\left(1-10^{-1}\right)$ to $\left(1-10^{-6}\right)$.  The whiskers denote the minimum and maximum mismatch over all templates.}
	\end{center}
\end{figure}
